### 2015-05-14 whoop.tex
space hack

Lockset instrumentation introduces: sets $\hasbeenread{i} \subseteq \powerset{\sharedvars}$ and $\hasbeenwritten{i} \subseteq \powerset{\sharedvars}$ to track the shared variables that have been read from and written to, respectively, by the thread executing $T$; a current lockset, $\currentlockset{i} \subseteq \powerset{\mutexes}$, to record the mutexes that are currently held by the thread; and, for each shared variable $s \in \sharedvars$, a lockset, $\lockset{s}{i}$, to record the mutexes that are consistently held when the thread accesses $s$.
%
The statements of each procedure in $\instrument{T}{i}$ that access shared variables and mutexes are instrumented to manipulate these sets, as shown in Figure~\ref{fig:instrumentation}.  For a shared variable assignment $s = e$ we record in $\hasbeenwritten{i}$ that $s$ has been written to, and update the lockset $\lockset{s}{i}$ to eliminate any mutexes that are not currently held (those mutexes that are not in $\currentlockset{i}$).  A shared variable read $x = s$ is instrumented analogously, with an additional $\havockeyword$ command which we discuss under \emph{Shared State Abstraction} below.  Instrumentation of mutex manipulation commands, $\mutexlock{m}$ and $\mutexunlock{m}$, involves updating the current lockset, $\currentlockset{i}$, to add and remove mutex $m$, respectively.

>>>>

Lockset instrumentation introduces: sets $\hasbeenread{i} \subseteq \powerset{\sharedvars}$ and $\hasbeenwritten{i} \subseteq \powerset{\sharedvars}$ to track the shared variables that have been read from and written to, respectively, by the thread executing $T$; a current lockset $\currentlockset{i} \subseteq \powerset{\mutexes}$ to record the mutexes currently held by the thread; and, for each shared variable $s \in \sharedvars$, a lockset $\lockset{s}{i}$ to record the mutexes that are consistently held when the thread accesses $s$.
%
The statements of each procedure in $\instrument{T}{i}$ that access shared variables and mutexes are instrumented to manipulate these sets, as shown in Figure~\ref{fig:instrumentation}.  For a shared variable assignment $s = e$, we record in $\hasbeenwritten{i}$ that $s$ has been written to, and update $\lockset{s}{i}$ to eliminate any mutexes that are not currently held (those mutexes that are not in $\currentlockset{i}$).  A shared variable read $x = s$ is instrumented analogously, with an additional $\havockeyword$ command which we discuss below.  Instrumentation of mutex manipulation commands, $\mutexlock{m}$ and $\mutexunlock{m}$, involves updating $\currentlockset{i}$ to add and remove mutex $m$, respectively.
